\documentclass{manolo}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}

\setlength{\parindent}{0pt}
\setlength{\parskip}{\baselineskip}
\graphicspath{{figures/}}

\newcommand{\term}[1]{\textit{#1}}
\newcommand{\quotes}[1]{`#1'}

\newcommand{\mycomment}[2]{\textbf{[#1]:} #2}

\title{Data Inspection and Generation v.1}
\deliverable{2.1}
\version{1}
\lead{NCSR}
\submission{Draft}


\begin{document}

\maketitle

\begin{NiceTabular}{m{0.26\textwidth}m{0.72\textwidth}}[colortbl-like]
\CodeBefore
  \rowcolor{mylblue}{3,5,7}
  \cellcolor{myblue}{3-1}
  \cellcolor{myblue}{4-1}
  \cellcolor{myblue}{5-1}
  \cellcolor{myblue}{6-1}
  \cellcolor{myblue}{7-1}
\Body
\multicolumn{2}{l}{\textcolor{myblue}{\bf Document Information}} \\
\multicolumn{2}{l}{} \\
\textcolor{white}{Issued by:}   & \thelead         \\
\textcolor{white}{Issue date:}  & \thesubmission   \\
\textcolor{white}{Due date:}    & 31 December 2024 \\
\textcolor{white}{Work package leader:} & NCSR     \\
\textcolor{white}{Dissemination level:} & Public   \\
\end{NiceTabular}

\vskip 3em

\begin{NiceTabular}{m{0.14\textwidth}m{0.2\textwidth}m{0.64\textwidth}}[colortbl-like]
\CodeBefore
  \rowcolor{white}{1,2}
  \rowcolor{myblue}{3}
  \rowcolor{mylblue}{4,6}
\Body
\multicolumn{3}{l}{\textcolor{myblue}{\bf Document History}} \\
\multicolumn{3}{l}{} \\
\textcolor{white}{Version} &
\textcolor{white}{Date} &
\textcolor{white}{Modifications made by} \\
0.1 & June 2024 & Document structure by NCSR \\
0.2 &           & \\
0.3 &           & \\
\end{NiceTabular}

\vskip 3em

\begin{NiceTabular}{m{0.69\textwidth}m{0.29\textwidth}}[colortbl-like]
\CodeBefore
  \rowcolor{white}{1,2}
  \rowcolor{myblue}{3}
  \rowcolor{mylblue}{4,6,8}
\Body
\multicolumn{2}{l}{\textcolor{myblue}{\bf Authors}} \\
\multicolumn{2}{l}{} \\
\textcolor{white}{Name} &
\textcolor{white}{Beneficiary} \\
S. Konstantopoulos, N. Koliou & NCSR \\
                              & NUIDUCD – CeADAR \\
                              & ARX.net \\
                              & FDI \\
                              & ATOS \\
\end{NiceTabular}


\noindent
In case you want any additional information, or you want to consult
with the authors of this document, please send your inquiries to:
konstant@iit.demokritos.gr

\vskip 3em

\begin{NiceTabular}{m{0.69\textwidth}m{0.29\textwidth}}[colortbl-like]
\CodeBefore
  \rowcolor{white}{1,2}
  \rowcolor{myblue}{3}
  \rowcolor{mylblue}{4}
\Body
\multicolumn{2}{l}{\textcolor{myblue}{\bf Quality Reviewers}} \\
\multicolumn{2}{l}{} \\
\textcolor{white}{Name} &
\textcolor{white}{Beneficiary} \\
Name  & Partner \\
Name  & Partner \\
\end{NiceTabular}

\vfill

\begin{NiceTabular}{m{0.98\textwidth}}[colortbl-like]
\CodeBefore
\rowcolor{mylblue}{1,2,4,5}
\Body
\bf Disclaimer \\
Funded by the European Union under GA no. 101135782. Views
and opinions expressed are however those of the authors only and do
not necessarily reflect those of the European Union or CNECT. Neither
the European Union nor the granting authority can be held responsible
for them. \\
\\
\bf \copyright MANOLO Consortium, 2024 \\
Reproduction is authorised provided the source is acknowledged. \\
\end{NiceTabular}

\clearpage

\tableofcontents

\clearpage

\listoffigures


\listoftables

\clearpage

\begin{NiceTabular}{m{0.19\textwidth}m{0.79\textwidth}}[colortbl-like]
\CodeBefore
  \rowcolor{white}{1,2}
  \rowcolor{myblue}{3}
  \rowcolor{mylblue}{4}
\Body
\multicolumn{2}{l}{\textcolor{myblue}{\bf List of Terms and Definitions}} \\
\multicolumn{2}{l}{} \\
\textcolor{white}{Term} &
\textcolor{white}{Definition} \\
My Term           &
This is a term \\
Machine Learning  &
This is another term \\
\end{NiceTabular}


\section*{Executive Summary}

This is a summary


\clearpage

\section{Introduction}

\subsection{Scope of Deliverable}

This report, titled \quotes{Data Inspection and Generation v.1},
documents research \& development work carried out in WP2 during
Phase~2 \emph{MANOLO Framework Implementation} of the project's
workplan.

Besides the report itself, the scope of this deliverable also comprises
the intermediate versions of the following software components:
%
\begin{itemize}
\item The \emph{Data Operations Manager}
\item The \emph{Data Quality Estimation Component}
\item The \emph{Data Distillation and Synthesis Component}
\end{itemize}

Work in WP2 also includes preparing and ingesting the use case
datasets in the data operations manager, but this is outside the scope
of this version of the deliverable and will be reported in v.2 (M24).

\subsection{Structure of Deliverable}

Taking the above into consideration, this remainder of this document
is structured as follows:
%
\begin{itemize}
\item Section~\ref{sec:datmgmt}: MANOLO presents to its cloud-edge operators
  a complicated provenance and lineage environment where the different
  assets, i.e., datasets, algorithms, models, resources are multiply
  interlinked, providing explanation of the capacities, data, metadata
  and their relationships. For regulatory as well as pragmatic
  reasons, MANOLO will need to ensure that project assets are
  integrated with the MANOLO data (assets) management sub-system, so
  that provenance and lineage metadata is automatically maintained.
  The Data Operations Manager will manage this functionality and
  expose APIs which will be supporting the overall project and MANOLO
  research and toolset.
\item Section~\ref{sec:datqual}: Mechanisms for data quality estimation will
  be developed, tested and integrated in this component by focussing
  on detecting and correcting anomalous data and automatically
  annotating data in terms of quality. Mechanisms for noise detection
  (including biased data due to gender, race, or other variables) as
  well as data maliciously manipulated will be given a special
  emphasis, employing adversarial machine learning while considering
  associated models.
\item Sections~\ref{sec:datdist} to~\ref{sec:featextr}:
  Techniques for data distillation will be
  explored here such that will provide a good foundation and a richer
  dataset to support the research in the Hardware-aware Model Training
  and Optimisation component. This will produce new derived
  (synthetic) data using methods for distillation via data compression
  and hashing, feature extraction and synthesisation; and model
  inversion for synthesisation of data from labels. Data compression
  will ensure the reduction of storage necessities as well as a
  faster, while accurate, training pipelines and lighter
  models. Feature extraction and synthesisation will allow us to
  propose meta-data for meta learning tasks. The creation of synthetic
  data from labels is a technique that will help us gather reliable
  datasets from accurate pretrained architectures to keep a useful
  repository for their application to posterior training processes
  where data are not satisfactory for quality, quantity or
  availability due to ethical reasons.
\end{itemize}

\clearpage
\section{Data Management and Provenance Framework}
\label{sec:datmgmt}
\input{task1}

\clearpage
\section{Data Quality Estimation}
\label{sec:datqual}
\input{task2}

\clearpage
\section{Data Distillation}
\label{sec:datdist}
\input{task3-distillation}

\clearpage
\section{Data and Feature Synthetisation}
\label{sec:datsynth}
\input{task3-synthesis}

\clearpage
\section{Feature Extraction}
\label{sec:featextr}
\input{task3-extraction}

\clearpage
\section{Conclusion}

\end{document}
