% (M5-M24) Leader: NCSR "D"
% CeADAR, UPC, ATOS, EVIDEN, FDI, INRIA, ARCADA, use case partners

\section{Introduction}

This task will implement a range of methods for automatically
annotating data with respect to quality or possible unreliability.

We will explore anomaly detection and other noise detection methods
that will allow identifying biased, noisy, inconsistent, or in general
low-quality data, as well as data maliciously manipulated to
contaminate the model during training. For these purposes, data
augmentation techniques based on adversarial machine learning methods
(such as controlled noise contamination of the dataset) will be used.

\section{Related Work}

Anomaly detection and other prior works that are domain-agnostic or
easily transferrable.


\section{Directing Attention at Low-Quality Data}

Background on Attention and the Transformer.

Core idea: observing the trained Attention module can identify the
characteristics of signal where attention was \emph{not} directed.
The expectation is that (ideally) loss due to inconsistent data will
be handled by directing attention away from inconsistent data instead
of training the network to work around it.


\section{Data Augmentation and Adversarial ML}

\mycomment{Expected contributions}%
{CeADAR to contribute regarding data augmentation}


\section{Experiments on Timeseries Processing}

\mycomment{Expected contributions}%
{BitBrain to contribute regarding background work on EEG quality estimation.}

\mycomment{Expected contributions}%
{PAL and BitBrain to contribute regarding the experimental setup.}

\section{Experiments on Computer Vision}

\mycomment{Expected contributions}%
{ARX.NET to contribute regarding background work on image quality estimation.}

\mycomment{Expected contributions}%
{PAL and ARX.NET to contribute regarding the experimental setup.}


\section{Conclusions}

